---
title: "lab3"
author: "Stephanie Gluck"
date: "2/3/2020"
output: 
  html_document: 
    theme: cerulean
---

```{r setup, include=FALSE}
library(devtools)
dev_mode(T)
library(rio)
library(ggplot2)
library(tidyverse)
library(scales)
library(fivethirtyeight)
library(ggrepel)

theme_set(theme_minimal()) 

knitr::opts_chunk$set(echo = TRUE)
```

```{r load_data}

google_trends <- google_trends

tv_states <- tv_states

```

## Google trends data and plot

Create long Google data 

```{r google_data}

google_d_long <- google_trends %>% 
  pivot_longer(starts_with("hurricane_"), 
               names_to = "hurricane", 
               values_to = "trend") %>% 
  mutate(hurricane = as.factor(hurricane)) %>%  
  mutate(hurricane = recode(hurricane, "hurricane_harvey_us" = "Hurricane Harvey", 
         "hurricane_irma_us" = "Hurricane Irma", 
         "hurricane_maria_us" = "Hurricane Maria", 
         "hurricane_jose_us" = "Hurricane Jose")) 

levels(google_d_long$hurricane)

```

###  Plots

Change in trends for each hurricane over time, line plot  

```{r google_line_plot}

ggplot(google_d_long, aes(date, trend)) +
  geom_line(aes(color = hurricane), size = 1) + 
  scale_color_brewer("Hurricane", 
                    palette = "Dark2") +
  theme(legend.position = "bottom", 
        legend.title = element_blank()) +
  labs(x = "Date",
       y = "Hurricane Trend",
       title = "Change in Trends for Each Hurricane Over Time")
```

Change in trends for each hurricane over time, solid shape plot

```{r google_shape_plot}

ggplot(google_d_long, aes(date, trend)) +
  geom_ribbon(aes(ymin = 0, ymax = trend, fill = hurricane), alpha = 0.7) +
  scale_fill_brewer("Hurricane", 
                    palette = "Dark2") + 
  theme(legend.position = "bottom", 
        legend.title = element_blank()) +
  labs(x = "Date",
       y = "Hurricane Trend",
       title = "Change in Trends for Each Hurricane Over Time")
```

Change in trends for each hurricane over time, continous color heat map 

```{r google_heat_map}

#heat map for continous color 
ggplot(google_d_long, aes(date, hurricane, fill = trend)) + 
  geom_tile() + 
  scale_fill_distiller("Trend", 
                       palette = "YlGnBu", 
                       direction = -1) +
  labs(x = "Date",
       y = "Hurricane",
       title = "Change in Trends for Each Hurricane Over Time")
```

Add reference line to plot for dates that each hurricane made landfall

```{r google_plot_landfall, fig.width = 8,fig.height = 6}

date <- c("August 25, 2017", "September 10, 2017", "", "September 20, 2017")
hurricane <- c("Harvey landfall", "Irma landfall", "Jose landfall", "Maria landfall")

landfall <- data.frame(date, hurricane) %>% 
  mutate(date = lubridate::mdy(as.character(date)))

head(landfall)
str(landfall)

ggplot(google_d_long, aes(date, trend)) +
  geom_ribbon(aes(ymin = 0, ymax = trend, fill = hurricane), alpha = 0.7) +
  geom_vline(data = landfall, 
             mapping = aes(xintercept = date), 
             color = "gray30", linetype = "dashed") +
  theme_minimal(base_size = 15) +
  scale_fill_brewer("Hurricane", 
                    palette = "Dark2") +
  geom_text(data = landfall, 
            mapping = aes(x = date, y = 65, label = hurricane), 
            size = 4, angle = 90, 
            vjust = -0.5, hjust = 0,
            color = "gray30") + 
  theme(legend.position = "bottom", 
        legend.title = element_blank()) +
  labs(x = "Date",
       y = "Trend",
       title = "Change in Trends for Each Hurricane Over Time",
       subtitle = "With Date of Landfall for Each Hurricane")

```

## Replicate the "National cable news networks" plot 

```{r tv_data}

tv_data_long <- tv_states %>% 
  pivot_longer(-date, 
               names_to = "state", 
               values_to = "sentences") %>% 
  mutate(state = as.factor(state)) %>%  
  mutate(state = recode(state, "florida" = "Florida", 
         "texas" = "Texas", 
         "puerto_rico" = "Puerto Rico")) %>% 
  mutate(state = fct_relevel(state, "Florida", "Texas", "Puerto Rico"))

levels(tv_data_long$state)
str(tv_data_long)
```

"National cable news networks" Plot 

```{r tv_plot}
#pink, fc5285
#orange, ed723c
#blue, 3ec1c9

color_palette <- c("#fc5285", "#ed723c", "#3ec1c9")

date <- c("August 25, 2017", "September 20, 2017", "October 1, 2017")
events <- c("Harvey\nlandfall", "Maria\nlandfall", "Las Vegas\nshooting")

key_dates <- data.frame(date, events) %>% 
  mutate(date = lubridate::mdy(as.character(date)))

head(key_dates)
str(key_dates)

date <- c("September 10, 2017")
events <- c("Irma\nlandfall")

irma_date <- data.frame(date, events) %>% 
  mutate(date = lubridate::mdy(as.character(date)))

ggplot(tv_data_long, aes(date, sentences)) +
  geom_ribbon(aes(ymin = 0, ymax = sentences, fill = state)) + 
  scale_fill_manual(values = color_palette) +
  theme_minimal(base_size = 15) +
  geom_vline(data = key_dates, 
             mapping = aes(xintercept = date), 
             color = "gray40", linetype = "dotted") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5), 
        axis.ticks = element_blank(), 
        panel.border = element_blank(), 
        panel.grid.minor = element_blank()) +
  labs(x = "",
       y = "Share of Sentences",
       title = "National cable news networks") +
  geom_label(data = key_dates, 
            mapping = aes(x = date, y = 3.4, label = events),
            size = 4, label.size = NA, 
            color = "gray40") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1, scale = 1)) + 
  geom_hline(yintercept = 0, color = "black") +
  annotate("text", x = as.Date("2017-08-29"), y = 1, 
           label = "Texas", color = "black", 
           fontface = "bold") +
  annotate("text", x = as.Date("2017-09-10"), y = 1.6, 
           label = "Florida", color = "black", 
           fontface = "bold") +
  annotate("text", x = as.Date("2017-09-30"), y = 1.6, 
           label = "Puerto Rico", color = "black", 
           fontface = "bold") + 
  geom_vline(data = irma_date, 
             mapping = aes(xintercept = date), 
             color = "gray40", linetype = "dotted") +
  geom_label(data = irma_date, 
            mapping = aes(x = date, y = 3.4, label = events),
            size = 4, label.size = NA, 
            color = "gray40", hjust = -.05) + 
   scale_x_date(limits = as.Date(c("2017-08-15","2017-10-10")), 
                breaks = as.Date(c("2017-08-15", "2017-09-01", "2017-09-15", "2017-10-01")), 
                labels = c("Aug. 15, 2017", "Sept. 1", "Sept. 15", "Oct. 1"))

```

```{r load_comic_data, include = F}
library(tidyverse)
library(lubridate)
library(janitor)

# Get DC characters:
comic_characters_dc <- 
  "https://github.com/fivethirtyeight/data/raw/master/comic-characters/dc-wikia-data.csv" %>% 
  read_csv() %>% 
  clean_names() %>% 
  mutate(publisher = "DC")

# Get Marvel characters:
comic_characters_marvel <- 
  "https://github.com/fivethirtyeight/data/raw/master/comic-characters/marvel-wikia-data.csv" %>% 
  read_csv() %>% 
  clean_names() %>% 
  mutate(publisher = "Marvel")

# Merge two dataset and perform further data wrangling:
comic_characters <-
  comic_characters_dc %>% 
  bind_rows(comic_characters_marvel) %>% 
  separate(first_appearance, c("year2", "month"), ", ", remove = FALSE) %>%
  mutate(
    # If month was missing, set as January and day as 01:
    month = ifelse(is.na(month), "01", month),
    day = "01",
    # Note some years missing:
    date = ymd(paste(year, month, day, sep = "-")),
    align = factor(
      align, 
      levels = c("Bad Characters", "Reformed Criminals", "Netural Characters", "Good Characters"),
      ordered = TRUE)
  ) %>%
  select(publisher, everything(), -c(year2, day))

rm(comic_characters_dc, comic_characters_marvel)

```


## Comic character visualization 

Data tidying 

```{r}

Hmisc::describe(comic_characters$sex)

#Will only include sex male & female as there is not enough characters in the other gender groups. 

#remove NAs from sex, filter for only male and female, clean up name
comic_d <- comic_characters %>% 
  filter(!is.na(sex)) %>% 
  mutate(name = str_replace(name, " \\(.*\\)", ""), 
         sex = str_replace(sex, " .*", "")) %>% 
  filter(sex == "Male" | sex == "Female") %>% 
  mutate(sex = as.factor(sex))

Hmisc::describe(comic_d$sex)

```

### Comic Plot 1 
```{r comic_plot1}
variable.names(comic_d)

ggplot(comic_d, aes(date, fill = sex)) +
  geom_histogram(bins = 15, 
                 color = "white") + 
  facet_wrap(~sex) + 
  scale_fill_brewer(palette = "Set1") + 
   theme(legend.position = "none", 
         plot.margin = margin(.5, 1, 0, .5, "cm"), 
         plot.title.position = "plot") +
  labs(x = "",
       y = "Number of Characters",
       title = "New Male and Female Comic Book Characters Introduced Per Year", 
       subtitle = "Number of characters collapsed across Marvel and DC comics") 

```

### Comic Plot 2 

```{r comic_plot2}

comic_top20 <- comic_d %>% group_by(publisher) %>% 
  top_n(20, wt = appearances) %>% 
  ungroup()

comic_top20 %>% group_by(publisher, sex) %>% 
  summarize(n = n()) 

female_name <- comic_top20 %>% 
  filter(sex == "Female") %>% 
  top_n(5, wt = appearances)

top5_name <- comic_top20 %>% 
  top_n(5, wt = appearances)

ggplot(comic_top20, aes(reorder(name, appearances), appearances, group = sex)) +
  geom_point(aes(color = sex), size = 3, alpha = 0.7) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        legend.position = "bottom",
        legend.title = element_blank(),
        panel.grid = element_blank()) + 
  geom_text_repel(data = female_name, aes(label = name), color = "#e41a1c") +
  geom_text_repel(data = top5_name, aes(label = name), color = "#377eb8") + 
  scale_color_brewer(palette = "Set1") + 
  labs(x = "Character Name",
       y = "Number of Appearances",
       title = "Top 20 Appearance for Marvel and DC Characters", 
       subtitle = "Name of top 5 appearing male and female characters printed") 

```

### Comic Plot 3 

```{r comic_plot3}

comic_align <- comic_d %>% group_by(align, sex) %>%  
  filter(str_detect(align, "Characters")) %>%
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = as.numeric(n)) %>% 
  pivot_wider(sex, names_from = align, values_from = n) %>% 
  mutate(tot = rowSums(.[2:3])) %>% 
  mutate(prop_bad = `Bad Characters` / tot, 
         prop_good = `Good Characters` / tot) %>% 
  pivot_longer(5:6, names_to = "align", values_to = "prop")

str(test)

variable.names(comic_align)
str(comic_align)

ggplot(comic_align, aes(x = sex, y = prop, fill = align)) +
  geom_bar(stat = "identity") +
  theme_minimal(base_size = 15) +
  theme(legend.position = "bottom", 
        legend.title = element_blank(), 
        plot.title.position = "plot") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_manual(values=c("#E69F00", "gray50"), 
                    breaks =c("prop_good", "prop_bad"),
                    labels =c("Good Characters", "Bad Characters")) +
  coord_flip() + 
  labs(x = "",
       y = "",
       title = "Percent of Good and Bad Characters by Gender", 
       subtitle = "Characters collapsed across Marvel and DC comics") 

```

